Highly Available Transactions: Virtues and Limitations

### 2013-03-21 writeup/evaluation.tex

>>>>

Thus far, we have largely ignored the question of which applications
actually require HAT semantics versus traditional ACID guarantees. As
we summarized in Section~\ref{needed}, the main cost of providing HAT
updates is the inability to prevent Lost Update, Write Skew, and
provide recency bounds. In this Section, we attempt to understand when
these guarantees matter both abstractly and by the use of a
representative customer order transaction application patterned off of
TPC-C.

Recent work on the CALM Theorem, Lattice-based state update, and
Commutative and Replicated Data Types demonstrates that, if updates
logically commute, then they can be performed in different orders at
different locations in a distributed system. Accordingly, as long as
all writes are delivered to all replicas, then a system executing
monotonic logic with commutative operators should not suffer from
application-level consistency anomalies as a result of Lost Update or
Write Skew anomalies. However, applications with non-monotonic state
mutation will not, in general, be able to maintain application-level
consistency constraints. Similarly, applications requiring
write visibility between clients should opt for unavailability instead
of possibly missing a write visibility deadline.

Absent a necessary and sufficient result describing exactly which
application logics can be achieved with high availability and to make
these requirements more concrete, we consider an example application:
the TPC-C benchmark. Our goal is \textit{not} to provide a performance
analysis, as any HAT configuration will be non-compliant. Rather, we
examine the five queries contained in the benchmarks---ostensibly
representative of a standard transaction processing application---to
understand which are achievable in a HAT context.

Integrity constraints:
--Mostly SUM, AVG, COUNT
--This is okay and foreign key constraints are provided by TA

New Order:
--Lookup of warehouse codes is fine, are not mutated
--Assigning a version order is not okay, but we can still get uniqueness
--Stock adjustment is monotonic and can't go below zero due to replenish. However, might overstock!

Payment:
--Monotonic, simply increase the number of each respective field

Delivery:
--Problematic; is non-monotonic, removing from the order table
--Without additional semantics, have to block
--CALM analysis would catch this, enforce coordination
--Does \textit{not} block new New Order transactions

Order Status:
--Non-monotonic
--Read your writes may be problematic

While TPC-C isolation tests are for lock-based models (and HATs are,
by requirement, non-locking), consider TPC-E tests. Modifying the
description and image together is fine, etc.
